---
title: "deliverable1"
output: html_document
---
Creating my data frame (tibble) that I am going to use for
my first deliverable. I have renamed columns to make them
easier to reference. I used the first initial of each
word to shorten the name.

```{r}
suppressMessages(library(tidyverse))
suppressMessages(library(tidyr))

data <- read_csv("LeagueofLegends.csv")
tData <- dplyr::tibble(region=data$League,
    year=data$Year,winner = data$bResult,
    blueTeam=data$blueTeamTag,
    redTeam=data$redTeamTag, gameTime = data$gamelength,
    bTC=data$blueTopChamp, bJC=data$blueJungleChamp,
    bMC=data$blueMiddleChamp, bADC=data$blueADCChamp,
    bSC=data$redSupportChamp,
    bT=data$blueTop, bJ=data$blueJungle, bM=data$blueMiddle,
    bAD=data$blueADC, bS=data$blueSupport,
    rTC=data$redTopChamp, rJC=data$redJungleChamp,
    rMC=data$redMiddleChamp, rADC=data$redADCChamp,
    rSC=data$redSupportChamp,
    rT=data$redTop, rJ=data$redJungle, rM=data$redMiddle,
    rAD=data$redADC, rS=data$redSupport)
```

I am creating four new columns, these columns will 
contain lists of the players/champions that 
participated in the games to make it easier to
calculate the win percentage and other factors.

I generated

```{r}

tData["redPlayers"] <- NA
tData["bluePlayers"] <- NA
tData["redChamps"] <- NA
tData["blueChamps"] <- NA

for(i in 1:nrow(tData)){
  tData$redPlayers[i] <- paste(tData$rT[i],
      tData$rJ[i], tData$rM[i], tData$rAD[i],
      tData$rS[i] ,sep=", ")
  
  tData$bluePlayers[i] <- paste(tData$bT[i],
      tData$bJ[i], tData$bM[i], tData$bAD[i],
      tData$bS[i] ,sep=", ")
  
  tData$redChamps[i] <- paste(tData$rTC[i],
      tData$rJC[i], tData$rMC[i], tData$rADC[i],
      tData$rSC[i] ,sep=", ")
  
   tData$blueChamps[i] <- paste(tData$bTC[i],
      tData$bJC[i], tData$bMC[i], tData$bADC[i],
      tData$bSC[i] ,sep=", ")
}
##> str_detect(df$redPlayers[23], RedPlayers[1])


```

I created lists that contain each Pro Player that is
referenced in here, and calculated their number of wins,total number of wins, and win percentage..
And also did the same with the Champs that were played, this helped to create some more continuous variables with which to create some visuals with.
```{r}
BluePlayers <- unique(c(unique(tData$bT), unique(tData$bJ), unique(tData$bM), unique(tData$bAD), unique(tData$bS)))
                     
RedPlayers <- unique(c(unique(tData$rT), unique(tData$rJ), unique(tData$rM), unique(tData$rAD), unique(tData$rS)))

BlueChamps <- unique(c(unique(tData$bTC), unique(tData$bJC), unique(tData$bMC), unique(tData$bADC), unique(tData$bSC)))
                     
RedChamps <- unique(c(unique(tData$rTC), unique(tData$rJC), unique(tData$rMC), unique(tData$rADC), unique(tData$rSC)))

Players <- data.frame(Player=c(RedPlayers,BluePlayers),wins=0, games=0, winPct = 0)

Champs <- data.frame(Champ= c(RedChamps,BlueChamps), wins=0, games=0, winPct = 0)

Players <- unique(Players)
Champs <- unique(Champs)

for (i in 1:nrow(tData)){
  for(j in 1:length(RedPlayers)){
  if(str_detect(tData$redPlayers[i], RedPlayers[j])){
    if(tData$winner[i] == 0){
    Players$wins[Players$Player==RedPlayers[j]]<- Players$wins[Players$Player==RedPlayers[j]] + 1
  }
    Players$games[Players$Player==RedPlayers[j]]<- Players$games[Players$Player==RedPlayers[j]] + 1
  }
}   
}

for (i in 1:nrow(tData)){
  for(j in 1:length(BluePlayers)){
  if(str_detect(tData$bluePlayers[i], BluePlayers[j])){
    if(tData$winner[i] == 1){
    Players$wins[Players$Player==BluePlayers[j]]<- Players$wins[Players$Player==BluePlayers[j]] + 1
  }
    Players$games[Players$Player==BluePlayers[j]]<- Players$games[Players$Player==BluePlayers[j]] + 1
  }
}   
}

for (i in 1:nrow(tData)){
  for(j in 1:length(RedChamps)){
  if(str_detect(tData$redChamps[i], RedChamps[j])){
    if(tData$winner[i] == 0){
    Champs$wins[Champs$Champ==RedChamps[j]]<- Champs$wins[Champs$Champ==RedChamps[j]] + 1
  }
    Champs$games[Champs$Champ==RedChamps[j]]<- Champs$games[Champs$Champ==RedChamps[j]] + 1
  }
}   
}

for (i in 1:nrow(tData)){
  for(j in 1:length(BlueChamps)){
  if(str_detect(tData$blueChamps[i], BlueChamps[j])){
    if(tData$winner[i] == 1){
    Champs$wins[Champs$Champ==BlueChamps[j]]<- Champs$wins[Champs$Champ==BlueChamps[j]] + 1
  }
    Champs$games[Champs$Champ==BlueChamps[j]]<- Champs$games[Champs$Champ==BlueChamps[j]] + 1
  }
}   
}

Players$winPct <- Players$wins / Players$games
Champs$winPct <- Champs$wins / Champs$games

```