---
title: "Discovery and Data Prep"
output: html_notebook
---

There are a number of variables that I am using, they are
all very similar to each other. The 20 main variables are
the players that are in each game along with the champions
that they played in those games. There are five players
per team and each player plays their own champion.
There different roles are Top, Jungle, Middle, ADC, and
Support. The two teams are red and blue. The variables I
created use the first letter of each word to shorten it.
I.E. Red side Top Laner is called rT, and the champion 
that they played is labeled as rTC where C stands for 
champion. The other variables I used were which teams 
participated in the games, one for each side. The length
of the game in minutes, and the winner of the game were 
two more variables used. The last two variables were the
years that the games took place as well as the region or
tournament that the game was played in.

[Here](https://www.google.com) is the link to the R code I used and some comments about how I created and cleaned my data.


## Visuals for Deliverable 1

# Win percentage of each player
These players all have more than 100 Games played

```{r}
Players100 <- filter(Players, games > 100)
Players100$Player <- factor(Players100$Player, levels = Players100$Player[order(Players100$winPct)])
ggplot(Players100, aes(x = Player, y = winPct)) + theme(axis.text.x=element_text(angle=45, size = rel(0.75), margin = margin(0.5, unit = "cm"))) + geom_col()
```

The graph is slightly hard to see so here are the top win
percentages and the lowest win percentages out of people that have over 100 games
```{r}
head(Players100[order(Players100$winPct),])

tail(Players100[order(Players100$winPct),])
```

# Number of times each champion was picked
These are the counts of how many times each champion was picked in competitive matches

```{r}
Champs$Champ <- factor(Champs$Champ, levels = Champs$Champ[order(Champs$games)])

ggplot(Champs, aes(x = Champ, y = games)) + theme(axis.text.x=element_text(angle=45, size = rel(0.75), margin = margin(0.5, unit = "cm"))) + geom_col()
```

Since the graph is a little cluttlered at the moment since every champion is added here is the least picked and most picked champs

```{r}
tail(Champs[order(Champs$games),])
head(Champs[order(Champs$games),])
```
