---
title: "Discovery and Data Prep"
output: html_notebook
---
## Deliverable 1

# Introduction

My Dataset is about League of Legends Professional matches and various stats about each game.

# The Data

I've used a subset of the data that I was given for this
first deliverable.

[Here](deliverable1.html) is the link to the R code
I used and some comments about how I created and cleaned
my data.

# Source
I retrieved my Data from kaggle and used it to created
some more variables based off of their data.

# In Depth of Variables

region - the Region that the match was played  
year  
winner  
blueTeam  
redTeam  
gameTime  
*The rest of the variables can be described as  
staring with r -> red team  
starting with b-> blue team  
ending with C meaning they are a Champion  
not ending with C meaning the Player  
T -> Top  
J -> Jungle  
M -> Middle  
AD -> Marksman  
S -> Support  
the last four variables are the lists of champs/players
that I used to help more easily create my data.  

## Visuals for Deliverable 1

# Win percentage of each player
These players all have more than 100 Games played

```{r}
Players100 <- filter(Players, games > 100)
Players100$Player <- factor(Players100$Player, levels = Players100$Player[order(Players100$winPct)])
ggplot(Players100, aes(x = Player, y = winPct)) + theme(axis.text.x=element_text(angle=45, size = rel(0.75), margin = margin(0.5, unit = "cm"))) + geom_col()
```

The graph is slightly hard to see so here are the top win
percentages and the lowest win percentages out of people that have over 100 games
```{r}
head(Players100[order(Players100$winPct),])

tail(Players100[order(Players100$winPct),])
```

# Number of times each champion was picked
These are the counts of how many times each champion was picked in competitive matches

```{r}
Champs$Champ <- factor(Champs$Champ, levels = Champs$Champ[order(Champs$games)])

ggplot(Champs, aes(x = Champ, y = games)) + theme(axis.text.x=element_text(angle=45, size = rel(0.75), margin = margin(0.5, unit = "cm"))) + geom_col()
```

Since the graph is a little cluttered at the moment since
every champion is added, here is the least picked and
most picked champs

```{r}
head(Champs[order(Champs$games),])

tail(Champs[order(Champs$games),])
```


## Future Questions

Some things I want to look into is how champion win rates and player win rates have changed over time

Right now I only have them clumped into the same category, I will need to split up the statistics by the year the game was played.

Another thing that I want to look at is the average game time with respect to the gold differences/towers/dragons/barons and kills.

One thing that I can't look into is what updates were released about the game. Some updates have been known to extend/reduce game times. 

Individual champions have also had changes to them that will affect how good they are resulting in either a higher or lower win rate.
